Sequence Divergence as the main modulator of structure-sequence correlations

### 2014-11-12 manuscript/cordiv.tex
some minor changes in seach for structural differences between viral and cellular proteins.

\vfill
\Title{Sequence Divergence as the main modulator of structure-sequence correlations}
\vfill
\Author{Amir Shahmoradi, Claus Wilke, Eleisha Jackson, ...}%\support}
\Address{\affiliation}
\vfill
\begin{Abstract}
    Over the past decade several independent works have shown that some site-specific structural properties of proteins are capable of predicting the site-specific evolutionary sequence variations. The strength and significance of these structure-evolution relations, however, appear to vary widely among different proteins, with correlations ranging from $0.1$ to $0.8$. In search for potential determinants of the observed variation in sequence-structure correlations, here we present the results of a comprehensive study of interrelations among more than $200$ structural and evolutionary characteristics in a dataset of 209 monomeric enzymes. We identify sequence divergence as the main determinant of the strengths of virtually all structure-evolution relationships.
\end{Abstract}
\vfill
\vfill
\end{titlepage}
\def\thefootnote{\fnsymbol{footnote}}
\setcounter{footnote}{0}
%

>>>>

\vfill
\Title{Sequence Divergence as the main modulator of structure-sequence correlations}
\vfill
\Author{Amir Shahmoradi, Claus Wilke, Eleisha Jackson, ...}%\support}
\Address{\affiliation}
\vfill
\begin{Abstract}
    Over the past decade several independent works have shown that some site-specific structural properties of proteins are capable of predicting the site-specific evolutionary sequence variations. The strength and significance of these structure-evolution relations, however, appear to vary widely among different proteins, with absolute correlation strengths ranging from $0.1$ to $0.8$. In search for potential determinants of the observed variation in sequence-structure correlations, here we present the results of a comprehensive study of interrelations among more than $200$ structural and evolutionary characteristics in a dataset of 209 monomeric enzymes. We identify sequence divergence as the main determinant of the strengths of virtually all structure-evolution relationships, explaining $\sim10-30\%$ of observed variation in correlation strengths. In addition to sequence divergence, we identify several protein structural properties that are weakly but significantly coupled with the strength of sequence-structure relations. In particular, proteins with more homogeneous back-bone hydrogen bond energies, large fractions of helical secondary structures and low fraction of beta sheets tend to exhibit the strongest sequence-structure relations.
\end{Abstract}
\vfill
\vfill
\end{titlepage}
\def\thefootnote{\fnsymbol{footnote}}
\setcounter{footnote}{0}
%
